### 2014-03-31 trunk/paper_enahpc14/paper.tex
updates paper; adds two empty files for the redaction of COSMO-ART model description and setup.

\begin{abstract}
  In this paper we present  COSMO-ART, an extension of the operational
  weather  forecast  model  of   the  German  Weather  Service  (DWD),
  developed for  the evaluation of the interactions  of reactive gases
  and aerosol particles  with the state of atmosphere  at the regional
  scale. It  includes secondary aerosols,  directly emitted components
  like  soot,  mineral  dust,  sea  salt and  biological  material  as
  pollen. Processes such  as emissions, coagulation, condensation, dry
  deposition,  wet removal,  and sedimentation  of aerosols  are taken
  into account.   The overall performance  of this application  on HPC
  systems is  analysed by a  profiling and tracing study  to determine
  hotspots  and  identify   critical  paths.   Moreover,  we  describe
  measurement devices and energy-aware techniques employed to evaluate
  the  energy  footprint of  the  considered  application  and to  get
  detailed  insights about  power bottlenecks.   Our motivation  is to
  improve  corresponding  code sections  to  sustain high  performance
  while  minimizing energy-to-solution.   This preliminary  study sets
  the basis of broader  considerations to tackle challenges related to
  energy efficient high performance  computing in the framework of the
  Exa2Green project (\url{http://exa2green.eu/}).

@@

\section{COSMO coupled with ART extension}
\label{sec:1}
\subsection{Model description and set-up}
\label{subsec:1}
\input{Sec1:COSMO-ART.tex}

@@

@@

\begin{acknowledgements}
This  research  was  supported   by  the  Exa2Green  research  project
co-funded  under the  EU  7th Framework  Program  Future and  Emerging
Technologies (FET) Proactive Initiative: Minimising Energy Consumption
of Computing to  the Limit (MINECC).  The authors  would like to thank
the  High  Performance  and  High  Productivity  Computing  Initiative
(\url{www.hp2c.ch}).)
\end{acknowledgements}

>>>>

\begin{abstract}
  In this paper we present  COSMO-ART, an extension of the operational
  weather  forecast  model  of   the  German  Weather  Service  (DWD),
  developed for  the evaluation of the interactions  of reactive gases
  and aerosol particles  with the state of atmosphere  at the regional
  scale. It  includes secondary aerosols,  directly emitted components
  like  soot,  mineral  dust,  sea  salt and  biological  material  as
  pollen. Processes such  as emissions, coagulation, condensation, dry
  deposition,  wet removal,  and sedimentation  of aerosols  are taken
  into account.   The overall performance  of this application  on HPC
  systems is  analysed by a  profiling and tracing study  to determine
  hotspots  and  identify   critical  paths.   Moreover,  we  describe
  measurement devices and energy-aware techniques employed to evaluate
  the  energy  footprint of  the  considered  application  and to  get
  detailed  insights about  power bottlenecks.   Our motivation  is to
  improve  corresponding  code sections  to  sustain high  performance
  while  minimizing energy-to-solution.   This preliminary  study sets
  the basis of subsequent  considerations to tackle challenges related
  to energy  efficient high performance computing in  the framework of
  the Exa2Green project (\url{http://exa2green.eu/}).

@@

\section{The operational COSMO-ART}
\label{sec:1}
\subsection{Model description}
\label{subsec:1.1}
\input{Subsec_1.1:Model_Description.tex}

\subsection{Model setup}
\label{subsec:1.2}
\input{Subsec_1.2:Model_Setup.tex}

@@

\section{Conclusion}
\label{concl}

@@

\begin{acknowledgements}
This  research  was  supported   by  the  Exa2Green  research  project
co-funded  under the  EU  7th Framework  Program  Future and  Emerging
Technologies (FET) Proactive Initiative: Minimising Energy Consumption
of Computing to  the Limit (MINECC).  The authors  would like to thank
the  High  Performance  and  High  Productivity  Computing  Initiative
(\url{www.hp2c.ch}) for  results that will be  leveraged in subsequent
code refactoring.
\end{acknowledgements}
